Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-05-24 ms.tex
citation of @ARTICLE{1998NewA....3..137D,

@@

For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the values of mass, radius, and effective temperature, and also obtained the values of parallax from the original Hipparcos datasets \memoYF{cite something} to compute the distance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{model_planetaryB.pdf}
   \plotoneh{model_planetaryB.pdf}
   \caption{.}
  \label{fig:observability}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbhp]
   \plotoneh{radio_1Mp_5AU.pdf}
   \plotoneh{radio_5Mp_5AU.pdf}
   \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_J$ and 5$M_J$ at 1 AU and 5AU. Cross symbols indicate that the radio emission is not observable because cyclotron frequency is less than plasma density around the planet. }
  \label{fig:observability}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the values of mass, radius, and effective temperature, and also obtained the values of parallax from the original Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS} to compute thes distance.

@@
